\documentclass[12pt]{article}
% fontenc and inputenc must precede biblatex/csquotes (pdflatex).
% With lualatex these are harmless no-ops.
\usepackage[T1]{fontenc}
\usepackage[utf8]{inputenc}
% babel (british) activates british-oscola.lbx and its bibliography strings.
\usepackage[british]{babel}
\usepackage[style=oscola,terseinits=true]{biblatex}
\usepackage[style=british]{csquotes}

\newcommand{\model}{%
  \par\strut\llap{*~}}

% Helper: label for model output vs package output
\newcommand{\expected}[1]{\par\textbf{Expected:} #1}
\newcommand{\pkg}{\par\textbf{Package:} }

\setlength{\parindent}{0pt}
\setlength{\parskip}{1ex}

\addbibresource{oscola-examples.bib}

\title{OSCOLA Test Document\\
  \large Testing OSCOLA 4 (existing) and OSCOLA 5 (new) features}
\author{}

\begin{document}

\maketitle

This document tests both the existing entry-types from OSCOLA 4 and
the new features added for OSCOLA~5 compliance.  Each section shows
the expected output above the package's actual output.

% ==============================================================
\section{Existing features (regression tests)}
% ==============================================================

\subsection{Books}

\model Andrew Burrows, \emph{Remedies for Torts and Breach of
  Contract} (3rd edn, OUP 2004) 317.

\cite[317]{burrows04}.

\model Justine Pila, \enquote{The Value of Authorship in the Digital
  Environment} in William H Dutton and Paul W Jeffreys (eds),
\emph{World Wide Research: Reshaping the Sciences and Humanities in
  the Century of Information} (MIT Press 2010).

\cite{pila10}.

\model John Cartwright, \enquote{The Fiction of the
  \enquote{Reasonable Man}} in AG Castermans and others (eds),
\emph{Ex Libris Hans Nieuwenhuis} (Kluwer 2009).

\cite{cartwright09}.

[NB The above uses \texttt{crossref} in the \texttt{.bib} file.]

\subsection{Cases}

\model \emph{Boulton v Jones} (1857) 2 H\&N 564, 157 ER 232.

\cite{boulton57}.

\model \emph{Henly v Mayor of Lyme} (1828) 5 Bing 91, 107; 130 ER 995,
1001.

\cite[107|1001]{henly28}.

% ==============================================================
\section{OSCOLA 5 changes}
% ==============================================================

% ---------------------------------------------------------------
\subsection{Ibid abolished by default (OSCOLA 5 s~1.2.3)}
% ---------------------------------------------------------------

Repeated citations of the same source should produce the short-form
cross-citation, not \emph{ibid}.  The second footnote below must
\emph{not} read `ibid'.

\expected{%
  \textsuperscript{n}~Burrows (n~[prev]) 100.%
}

\pkg
\footcite[317]{burrows04}%
\footcite[100]{burrows04}.

To restore OSCOLA~4 ibid behaviour, pass \texttt{ibid=true} as a
package option.

% ---------------------------------------------------------------
\subsection{Thesis titles italicised (OSCOLA 5 s~3.7.6)}
% ---------------------------------------------------------------

\expected{%
  Javan Herberg, \emph{Injunctive Relief for Wrongful Termination of
  Employment} (DPhil thesis, University of Oxford 1989).%
}

\pkg
\cite{herberg89}.

% ---------------------------------------------------------------
\subsection{Newspaper articles — no city (OSCOLA 5 s~3.7.7)}
% ---------------------------------------------------------------

\expected{%
  Jane Croft, `Supreme Court Warns on Quality'
  \emph{Financial Times} (1 July 2010) 3.%
}

(The city `London' must \emph{not} appear.)

\pkg
\cite{croft}.

% ---------------------------------------------------------------
\subsection{ECLI as default for EU cases (OSCOLA 5 s~4.4.2)}
% ---------------------------------------------------------------

\expected{%
  Joined Cases~C-430/93 and C-431/93 \emph{Jereon van Schijndel v Stichting Pensioenfonds voor Fysiotherapeuten}
  EU:C:1995:441.%
}

(The ECR citation must \emph{not} appear when an ECLI is available.)

\pkg
\cite{C430/93}.

% ---------------------------------------------------------------
\subsection{Podcasts (OSCOLA 5 s~3.7.2)}
% ---------------------------------------------------------------

\expected{%
  Joe Bloggs, `Making Up the Law'
  (\emph{The Fictitious Law Pod}, 1 April 2023) 27:14--35:22
  \textlangle{}https://perma.cc/FAKE-PCST\textrangle.%
}

(No `accessed' date: Perma.cc URL. Timestamp appears after the date parens.)

\pkg
\cite[27:14--35:22]{bloggs:podcast23}.

% ---------------------------------------------------------------
\subsection{Social media posts (OSCOLA 5 s~3.7.1)}
% ---------------------------------------------------------------

\expected{%
  @The Criminal Bar (\emph{Twitter}, 26 June 2023, 9:13pm GMT+1)
  \textlangle{}https://perma.cc/HD6K-3GZQ\textrangle.%
}

(No `accessed' date: Perma.cc URL.)

\pkg
\cite{criminalbar:tweet23}.

% ---------------------------------------------------------------
\subsection{Book reviews (OSCOLA 5 s~3.5)}
% ---------------------------------------------------------------

\expected{%
  AG Guest, `An Introduction to the Law of Contract'
  (1961) 24 MLR 658 (book review).%
}

\pkg
\cite{guest:1961}.

\expected{%
  Donal Nolan, `Enterprise Liability and the Common Law'
  (2012) 41 ILJ 370 (book review).%
}

\pkg
\cite{nolan:2012}.

% ---------------------------------------------------------------
\subsection{Timestamp pinpoints (OSCOLA 5 s~3.1.3)}
% ---------------------------------------------------------------

The timestamp postnote must appear after the date parenthesis and
before the URL (not at the end of the citation).

\expected{%
  UK Supreme Court, `Lady Hale's Valedictory Remarks -- 18 December 2019'
  (\emph{YouTube}, 18 December 2019) 42:41--51:17
  \textlangle{}https://perma.cc/7YZV-Y43A\textrangle.%
}

\pkg
\cite[42:41--51:17]{uksc:hale19}.

% ---------------------------------------------------------------
\subsection{Perma.cc URLs — no `accessed' date
  (OSCOLA 5 s~3.1.4)}
% ---------------------------------------------------------------

A \texttt{urldate} field is present in the entry but must be
\emph{suppressed} because the URL begins with \texttt{perma.cc}.

\expected{%
  Cyclefree, `Is This Really Necessary, Minister?'
  (\emph{Legal Feminist}, 27 April 2023)
  \textlangle{}https://perma.cc/3THK-P4AX\textrangle.%
}

(No `accessed \ldots' text after the URL.)

\pkg
\cite{cyclefree:2023}.

Compare with a non-Perma.cc URL where `accessed' should still appear:

\expected{%
  Sarah Cole, `Virtual Friend Fires Employee' \emph{Naked Law}
  (1 May 2009) \textlangle{}\ldots\textrangle{} accessed 9 November 2009.%
}

\pkg
\cite{cole09}.

% ---------------------------------------------------------------
\subsection{Court rules — CrPR and FPR (OSCOLA 5 s~2.5.3)}
% ---------------------------------------------------------------

CrPR and FPR should be cited without SI number, and with the rule
number following directly (no `Order' prefix), just like CPR.

\expected{%
  CrPR r~17.}

\pkg
\cite[r~17]{crpr2020}.

\expected{%
  FPR r~4.1.}

\pkg
\cite[r~4.1]{fpr2010}.


% ---------------------------------------------------------------
\subsection{Assimilated EU law (OSCOLA 5 s~2.4.9)}
% ---------------------------------------------------------------

\expected{%
  Assimilated Regulation (EC) No 593/2008 \ldots\ [2008] OJ L177/6,
  as amended by SI 2019/834, reg~10.%
}

\pkg
\cite{rome1assimilated}.

% ---------------------------------------------------------------
\subsection{Scottish Court of Session — CSIH/CSOH implies the division
  (OSCOLA 5)}
% ---------------------------------------------------------------

When the neutral citation already names the division (CSIH or CSOH),
no separate IH/OH identifier should appear.

\expected{%
  \emph{Ponticelli Ltd v Gallagher} [2023] CSIH 32, 2023 SLT 823.%
}

\pkg
\cite{ponticelli23}.

When there is no neutral citation, the IH/OH designation must appear.

\expected{%
  \emph{Adams v Advocate General} 2003 SC 171 (OH), 175.%
}

\pkg
\cite[175]{adams03}.

% ---------------------------------------------------------------
\subsection{No terminal full stop in bibliography
  (OSCOLA 5 s~1.7)}
% ---------------------------------------------------------------

Check that entries in the bibliography below do \emph{not} end with a
full stop.

\section{Other changes}

% ---------------------------------------------------------------
\subsection{EU legislation: no page number (new OJ format)}
% ---------------------------------------------------------------

Newer editions of the OJ do not carry page numbers.  The series letter
(\texttt{L}, \texttt{C}, etc.)\ must appear without a trailing slash.

\expected{%
  Regulation (EU) 2025/783 of the European Parliament and of the Council
  of 14 April 2025 amending Regulation (EU) 2018/196 on additional customs
  duties on imports of certain products originating in the United States of
  America [2025] OJ L.%
}

\pkg
\cite{eu2025:tariffs}.

% ---------------------------------------------------------------
\subsection{Generative AI (OSCOLA 5 s~3.7.13)}
% ---------------------------------------------------------------

AI outputs: author is the AI name, prompt in inverted commas after
`response to', then organisation and date in parens.  No italics anywhere.

\expected{%
  ChatGPT, response to `Explain how artificial intelligence works',
  OpenAI (16 July 2023).%
}

\pkg
\cite{chatgpt:ai23a}.

\expected{%
  ChatGPT, response to `How to cite ChatGPT in the style of OSCOLA',
  OpenAI (16 July 2023).%
}

\pkg
\cite{chatgpt:ai23b}.

% ---------------------------------------------------------------
\subsection{Welsh Parliament legislation — asc/anaw/dccc numbers}
% ---------------------------------------------------------------

Acts of the National Assembly for Wales (\texttt{anaw}/\texttt{dccc})
and Welsh Parliament (\texttt{asc}) should print the number in
parentheses after the title and year.

\expected{%
  Deddf Trawsblannu Dynol (Cymru) 2013 (dccc~5).%
}

\pkg
\cite{transplantation13}.

\expected{%
  Child (Abolition of Defence of Reasonable Punishment) (Wales) Act 2020
  (anaw~3).%
}

\pkg
\cite{abolition20}.

\expected{%
  Welsh Tax Acts etc (Power to Modify) Act 2022 (asc~2).%
}

\pkg
\cite{welshtax22}.


\printbibliography

\end{document}

%%% Local Variables:
%%% coding: utf-8
%%% mode: LaTeX
%%% End:
